---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# viztoc

<!-- badges: start -->
<!-- badges: end -->

viztoc (visual table of contents) is for creating a visual summaries, especially of flipbooks or xaringan slides.  viztoc includes a variety of strategies for previewing slide contents.    In the html setting, a viztoc might be a gif, still, or still that becomes a gif if you hover over it -- then ideally, you can click through to the full flipbook/slideshow, or to the relevant page in the flipbook from the table of contents.  

- You can see one style of the "visual table of contents" here: https://evamaerey.github.io/ggplot_flipbook/ggplot_flipbook_xaringan.html#7  (the stills)

- And another here:  https://evamaerey.github.io/ggplot2_grammar_guide/about  (stills to gifs upon mouse over) - (this variety only collects the images produced by xaringan).

- Then, the entire slides as frames in gif: https://evamaerey.github.io/data_manipulation/about 


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("EvaMaeRey/viztoc")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(viztoc)
## basic example code
```

